#This is free, open-source software under the (lenient) GNU GPLv3. It comes with no warranty. It concerns synergy analysis of mixtures whose component IDER (Individual Dose Effect Relations) are SNTE as defined in the NASA report "Synergy Analyses for Mixed Radiation Fields That Induce Non-Targeted Effects", "our NASA report" for short. This script was written by Dae Woong Ham between Sept. 2016 and May 2017. Quality control by Rainer K. Sachs May-June 2017.

#The Data
```{r}
#All the libraries needed for this script
library(ggplot2) #library for plotting
library(deSolve) # library for solving differential equations
library(gridExtra) #for plotting
library(minpack.lm) #for non-linear regression package

#Create dataframes that store the data summarized in [Cacao E, M Hada, PB Saganti, KA George and FA Cucinotta. "Relative Biological Effectiveness of HZE Particles for Chromosomal Exchanges and Other Surrogate Cancer Risk Endpoints." PLoS One 11(4): e0153998. (2016)], "16Cacao" for short. 

Oxygen = data.frame(d = c(0, .0125, .02, .025, .05, .075, .1, .2, .4), 
                    CA = c(.24, 1.66, 2.43, 2.37, 1.16, 2.85, 2.58, 6.94, 6.91))

Si = data.frame(d = c(0, .02, .04, .06, .08, .1, .12, .2, .4, .8, 1.2), 
                    CA = c(.11, 1.26, 1.14, 1.58, 1.22, 1.89, 3.47, 4.6, 9.79, 27.01, 38.84))

Fe600 = data.frame(d = c(0, .01, .02, .04, .06, .08, .1, .12, .2, .4, .8), 
                     CA = c(.13, .76, .99, 1.2, 1.74, 1.28, 1.2, 1.7, 3.02, 5.52, 12.42))

Fe450 = data.frame(d = c(0, .02, .04, .06, .08, .1, .2, .4), 
                   CA = c(0, .86, .6, .8, 1.22, 2.02, 2.3, 4.77))

Fe300 = data.frame(d = c(0, .005, .01,  0.02, .04, .07, .1, .2, .4, .8), 
                   CA = c(0.41, 1.23, 1.47, 1.22, .97, 1.46, 1.21, 4.38, 6.22, 13.6))

Ti = data.frame(d = c(0,  0.02, .04, .06, .08, .1, .15, .3, .6), 
                   CA = c(0, 1.99, 1.88, 1.44, 2.67, 2.57, 2.50, 5.64, 11.19))

param = data.frame(ion = c("O", "Si", "Ti", "Fe600", "Fe450", "Fe300"),
                   Z = c(8, 14, 22, 26, 26, 26), L = c(75, 100, 125, 175, 195, 240), 
                   Z.beta = c(595, 690, 770, 1075, 1245, 1585))

#putting it in one big data frame
big_df = rbind(Oxygen, Si, Ti, Fe600, Fe450, Fe300)
big_df$Z = rep(param$Z, times = c(9, 11, 9, 11, 8, 10))
big_df$Z.beta = rep(param$Z.beta, times = c(9, 11, 9, 11, 8, 10))
big_df$L = rep(param$L, times = c(9, 11, 9, 11, 8, 10))
big_df$error = c(0.24, 0.63, 0.77, 0.75, 0.52, 0.82, 0.78, 1.31, 1.59, 0.12, 0.05, 0.07, 0.56, 0.18, 0.60, 1.23, 1.60, 1.55, 4.27, 7.21, 0, 0.70, 0.66, 0.59, 0.80, 0.78, 0.48, 1.15, 2.39, 0.16, 0.38, 0.24, 0.21, 0.02, 0.37, 0.54, 0.17, 0.55, 1.75, 2.59, 0, 0.43, 0.34, 0.40, 0.50, 0.64, 0.73, 1.09, 0.29, 0.55, 0.60, 0.55, 0.49, 0.60, 0.54, 1.03, 1.22, 3.62)
big_df$ion = rep(param$ion, times = c(9, 11, 9, 11, 8, 10))

#will modify the data frame to get rid of the zero dose points irrelevant to our main parameter estimation
modified_df = big_df[big_df$d != 0, ]
modified_df$CA = modified_df$CA*0.01
modified_df$error = modified_df$error*0.01
big_df$CA = big_df$CA * 0.01
big_df$error = big_df$error * 0.01
big_df$errorbar_lower = big_df$CA - big_df$error
big_df$errorbar_upper = big_df$CA + big_df$error
```

#NTE1 and NTE2 models in 16Cacao using their parameters
```{r}
#NTE1 function
NTE1_function = function(d, L, Z.beta, eta0 = 0.00011, eta1 = 0.007, sig0 = 6.12, kap = 796) {
0.0017 + eta0*L*exp(-eta1*L)*(d != 0) + 
    (6.242*(d/L))*(sig0*(1-exp(-Z.beta/kap))^2 + 0.041/6.24*L*(1 - (1-exp(-Z.beta/kap))^2))
} 

#NTE2 function
NTE2_function = function(d, L, Z.beta, eta0 = 0.00047, eta1 = 0.011, sig0 = 6.75, kap = 590) {
0.0017 + eta0*L*exp(-eta1*L)*exp(-(1012*(d/L)))*(d != 0) + 
    (6.242*(d/L))*(1-exp(-(1012*(d/L))))*
    (sig0*(1-exp(-Z.beta/kap))^2 + 0.041/6.24*L*(1 - (1-exp(-Z.beta/kap))^2))
} 
```

#SNTE IDER, Tables 2-4 in NASA report
```{r}
#our proposed function
IDER = function(d, L, Z.beta, eta0, eta1, sig0, kap) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  eta = eta0*L*exp(-eta1*L)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))
} 

#nls method to get the parameters needed (4 parameter estimation)
IDER_model = nlsLM(CA ~ IDER(d, L, Z.beta, eta0, eta1, sig0, kap), data = modified_df, start = list(eta0 = 0.001, eta1 = 0.01, sig0 = 5, kap = 500), 
weights = (1/(modified_df$error)^2))
coef(IDER_model)
#eta0 = 1.484687e-04, eta1 = 3.513927e-03, sig0 = 4.149660e+00, kap = 4.688287e+02
vcov(IDER_model)
summary(IDER_model, cor = TRUE)
```

#Information criteria (AIC and BIC) - table 5 
```{r}
#L_function gives the residuals squared
L_function = function(func, eta0, eta1, sig0, kap) {
  a = vector(length = 0)
  for (i in 1:length(modified_df[, 1])) {
    a = c(a, modified_df$CA[i] - func(d = modified_df$d[i], L = modified_df$L[i], Z.beta = modified_df$Z.beta[i], eta0 = eta0, eta1 = eta1, sig0 = sig0, kap = kap))
  }
  return(a^2)
}
L_NTE1 = L_function(NTE1_function, eta0 = 0.00011, eta1 = 0.007, sig0 = 6.12, kap = 796)
L_NTE2 = L_function(NTE2_function, eta0 = 0.00047, eta1 = 0.011, sig0 = 6.75, kap = 590)
L_IDER = L_function(IDER, eta0 = 1.484687e-04, eta1 = 3.513927e-03, sig0 = 4.149660e+00, kap = 4.688287e+02)

#Since all models both used in our NASA report and 16Cacao's are weighted least square regression, will weight it with our weights to get the WRSS (weighted residual squared sum)
WRSS_NTE1 = sum((1/modified_df$error^2)*L_NTE1)
WRSS_NTE2 = sum((1/modified_df$error^2)*L_NTE2)
WRSS_IDER = sum((1/modified_df$error^2)*L_IDER)

#Definition of AIC and BIC calculation for Weighted Least Square regression
AIC_function = function(RSS, k = 4, n = length(modified_df[ , 1])) {
  n + n*log(2*pi) + n*log(RSS/n) + 2*(k+1)
}

BIC_function = function(n = length(modified_df[, 1]), k = 4, RSS) {
  n + n*log(2*pi) + n*log(RSS/n) + log(n)*(k+1)
}

NTE1_AIC = AIC_function(RSS = WRSS_NTE1)
NTE2_AIC = AIC_function(RSS = WRSS_NTE2)
IDER_AIC = AIC_function(RSS = WRSS_IDER)
NTE1_BIC = BIC_function(RSS = WRSS_NTE1)
NTE2_BIC = BIC_function(RSS = WRSS_NTE2)
IDER_BIC = BIC_function(RSS = WRSS_IDER)
information_critera_df = data.frame(AIC = c(NTE1_AIC, NTE2_AIC, IDER_AIC), BIC = c(NTE1_BIC, NTE2_BIC, IDER_BIC), row.names = c("NTE1 model", "NTE2 model", "IDER model"))
information_critera_df
```

#Baseline no-synergy/no-antagonism MIXDER (mixed field dose-effect relation(s)) based on any input
```{r}
MIXDER_function = function(r, L, Z.beta, d = seq(0, 0.2, by = 0.001), eta0 = 1.484687e-04, eta1 = 3.513927e-03, sig0 = 4.149660e+00, kap = 4.688287e+02) {
  dE=function(yini,State,Pars){
  eta0 = eta0; eta1 = eta1; sig0 = sig0; kap = kap
  with(as.list(c(State, Pars)), {
    P = vector(length = length(L))
    sig = vector(length = length(L))
    etaa = vector(length = length(L))
    u = vector(length = length(L))
    for (i in 1:length(L)) {
      P[i] = (1-exp(-Z.beta[i]/kap))^2
      sig[i] = sig0*P[i] + 0.041/6.24*L[i]*(1-P[i])
      etaa[i] = eta0*L[i]*exp(-eta1*L[i])
      u[i] = uniroot(function(d) sig[i]*6.24*d/L[i]*(1-exp(-1024*d/L[i])) + etaa[i]*(1-exp(-10^5*d)) - I, lower = 0, upper = 1, extendInt = "yes", tol = 10^-10)$root 
    }
    dI = vector(length = length(L))
    for (i in 1:length(L)) {
      dI[i] = r[i]*(sig[i]*6.24/L[i]*exp(-1024*u[i]/L[i])*(exp(1024*u[i]/L[i]) + 1024*u[i]/L[i] - 1) + etaa[i]*10^5*exp(-10^5*u[i])) 
    }
    dI = sum(dI)
    return(list(c(dI)))
    })
  }
  pars = NULL; yini = c(I= 0); d = d
  out = ode(yini,times = d, dE, pars, method = "radau")
  return(out)
}
```

#Graphs for NTE1 and IDER model 12_ion figure
```{r, eval = F}
#When creating any sort of figures we use this IDER now without the background effect then add the background effect at the end.
IDER = function(d, L, Z.beta, eta0 = 1.484687e-04, eta1 = 3.513927e-03, sig0 = 4.149660e+00, kap = 4.688287e+02) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  eta = eta0*L*exp(-eta1*L)
  sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))
} 

#Comparing the NTE1 model in 16Cacao with our NASA SNTE model

#Use these dose points to generate the curves necessary. Had to include a lot more dose points at lower doses when it is very sensitive to change
d_O = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:40))
d_1 = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:15))

oxygen = ggplot() + geom_errorbar(data = big_df[1:9, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[1:9]*100, y = 100*big_df$CA[1:9])) + geom_line(aes(x = d_O * 100,  y = 100*(0.00071 + IDER(d = d_O, L = 75, Z.beta = 595)), col = "IDER model")) + geom_line(aes(x = d_O * 100, y = 100 * NTE1_function(d = d_O, L= 75, Z.beta = 595), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank())

oxygen_zoomout = ggplot() + geom_errorbar(data = big_df[1:7, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(aes(x = big_df$d[1:7]*100, y = 100*big_df$CA[1:7])) + geom_line(aes(x = d_1 * 100,  y = 100*(0.00071 + IDER(d = d_1, L = 75, Z.beta = 595)), col = "IDER model")) + geom_line(aes(x = d_1 * 100, y = 100*NTE1_function(d = d_1, L= 75, Z.beta = 595), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank()) + ylim(0, 4)

d_S = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:120))

silicon = ggplot() + geom_errorbar(data = big_df[10:20, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[10:20]*100, y = 100*big_df$CA[10:20])) + geom_line(aes(x = d_S * 100,  y = 100*(0.00071 + IDER(d = d_S, L = 100, Z.beta = 690)), col = "IDER model")) + geom_line(aes(x = d_S * 100, y = 100 * NTE1_function(d = d_S, L= 100, Z.beta = 690), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank())

silicon_zoomout = ggplot() + geom_errorbar(data = big_df[10:17, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(aes(x = big_df$d[10:17]*100, y = 100*big_df$CA[10:17])) + geom_line(aes(x = d_1 * 100,  y = 100*(0.00071 + IDER(d = d_1, L = 100, Z.beta = 690)), col = "IDER model")) + geom_line(aes(x = d_1 * 100, y = 100*NTE1_function(d = d_1, L= 100, Z.beta = 690), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank()) + ylim(0, 4) + xlim(0, 15)

d_t = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:60))

titanium = ggplot() + geom_errorbar(data = big_df[21:29, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[21:29]*100, y = 100*big_df$CA[21:29])) + geom_line(aes(x = d_t * 100,  y = 100*(0.00071 + IDER(d = d_t, L = 125, Z.beta = 770)), col = "IDER model")) + geom_line(aes(x = d_t * 100, y = 100 * NTE1_function(d = d_t, L= 125, Z.beta = 770), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank())

titanium_zoomout = ggplot() + geom_errorbar(data = big_df[21:27, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(aes(x = big_df$d[21:27]*100, y = 100*big_df$CA[21:27])) + geom_line(aes(x = d_1 * 100,  y = 100*(0.00071 + IDER(d = d_1, L = 125, Z.beta = 770)), col = "IDER model")) + geom_line(aes(x = d_1 * 100, y = 100*NTE1_function(d = d_1, L= 125, Z.beta = 770), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank()) + ylim(0, 4) + xlim(0, 15)

d_six = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:85))

iron_six = ggplot() + geom_errorbar(data = big_df[30:40, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[30:40]*100, y = 100*big_df$CA[30:40])) + geom_line(aes(x = d_six * 100,  y = 100*(0.00071 + IDER(d = d_six, L = 175, Z.beta = 1075)), col = "IDER model")) + geom_line(aes(x = d_six * 100, y = 100 * NTE1_function(d = d_six, L= 175, Z.beta = 1075), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank())

iron_six_zoomout = ggplot() + geom_errorbar(data = big_df[30:37, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(aes(x = big_df$d[30:37]*100, y = 100*big_df$CA[30:37])) + geom_line(aes(x = d_1 * 100,  y = 100*(0.00071 + IDER(d = d_1, L = 175, Z.beta = 1075)), col = "IDER model")) + geom_line(aes(x = d_1 * 100, y = 100*NTE1_function(d = d_1, L= 175, Z.beta = 1075), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank()) + ylim(0, 4) + xlim(0, 15)

d_four = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:45))

iron_four = ggplot() + geom_errorbar(data = big_df[41:48, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[41:48]*100, y = 100*big_df$CA[41:48])) + geom_line(aes(x = d_four * 100,  y = 100*(0.00071 + IDER(d = d_four, L = 195, Z.beta = 1245)), col = "IDER model")) + geom_line(aes(x = d_four * 100, y = 100 * NTE1_function(d = d_four, L= 195, Z.beta = 1245), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank())

iron_four_zoomout = ggplot() + geom_errorbar(data = big_df[41:46, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(aes(x = big_df$d[41:46]*100, y = 100*big_df$CA[41:46])) + geom_line(aes(x = d_1 * 100,  y = 100*(0.00071 + IDER(d = d_1, L = 195, Z.beta = 1245)), col = "IDER model")) + geom_line(aes(x = d_1 * 100, y = 100*NTE1_function(d = d_1, L= 195, Z.beta = 1245), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank()) + ylim(0, 4) + xlim(0, 15)

d_three = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:80))

iron_three = ggplot() + geom_errorbar(data = big_df[49:58, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[49:58]*100, y = 100*big_df$CA[49:58])) + geom_line(aes(x = d_three * 100,  y = 100*(0.00071 + IDER(d = d_three, L = 240, Z.beta = 1585)), col = "IDER model")) + geom_line(aes(x = d_three * 100, y = 100 * NTE1_function(d = d_three, L= 240, Z.beta = 1585), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank())

iron_three_zoomout = ggplot() + geom_errorbar(data = big_df[49:55, ], aes(x = d*100, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(aes(x = big_df$d[49:55]*100, y = 100*big_df$CA[49:55])) + geom_line(aes(x = d_1 * 100,  y = 100*(0.00071 + IDER(d = d_1, L = 240, Z.beta = 1585)), col = "IDER model")) + geom_line(aes(x = d_1 * 100, y = 100*NTE1_function(d = d_1, L= 240, Z.beta = 1585), col = "NTE1 model"), linetype = "dotted") + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + theme(axis.text.x = element_blank(), axis.text.y = element_blank()) + ylim(0, 4) + xlim(0, 15)

setEPS()
postscript("12_ions.eps", width = 10, height = 7)
grid.arrange(oxygen, silicon, titanium, oxygen_zoomout, silicon_zoomout, titanium_zoomout, iron_six, iron_four, iron_three, iron_six_zoomout, iron_four_zoomout, iron_three_zoomout, ncol = 3)
dev.off()
```

#Graphs for the NTE2 and IDER model comparison in Appendix A2 (zoomed in)
```{r, eval = F}
#Comparing the NTE2 in 16Cacao with our NASA SNTE model
O = ggplot() + geom_errorbar(data = big_df[1:9, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[1:9], y = big_df$CA[1:9])) + geom_line(aes(x = d_O,  y = 0.00071 + IDER(d = d_O, L = 75, Z.beta = 595), col = "IDER model")) + geom_line(aes(x = d_O, y = NTE2_function(d = d_O, L= 75, Z.beta = 595), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

S = ggplot() + geom_errorbar(data = big_df[10:20, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[10:20], y = big_df$CA[10:20])) + geom_line(aes(x = d_S,  y = 0.00071 + IDER(d = d_S, L = 100, Z.beta = 690), col = "IDER model")) + geom_line(aes(x = d_S, y = NTE2_function(d = d_S, L= 100, Z.beta = 690), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank()) + xlim(0, 0.4) + ylim(0,0.12)

Ti = ggplot() + geom_errorbar(data = big_df[21:29, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[21:29], y = big_df$CA[21:29])) + geom_line(aes(x = d_t,  y = 0.00071 + IDER(d = d_t, L = 125, Z.beta = 770), col = "IDER model")) + geom_line(aes(x = d_t, y = NTE2_function(d = d_t, L= 125, Z.beta = 770), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank()) + xlim(0, 0.4) + ylim(0, 0.075)

i_6 = ggplot() + geom_errorbar(data = big_df[30:40, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[30:40], y = big_df$CA[30:40])) + geom_line(aes(x = d_six,  y = 0.00071 + IDER(d = d_six, L = 175, Z.beta = 1075), col = "IDER model")) + geom_line(aes(x = d_six, y = NTE2_function(d = d_six, L= 175, Z.beta = 1075), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank()) + xlim(0, 0.4) + ylim(0, 0.06)

i_4 = ggplot() + geom_errorbar(data = big_df[41:48, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[41:48], y = big_df$CA[41:48])) + geom_line(aes(x = d_four,  y = 0.00071 + IDER(d = d_four, L = 195, Z.beta = 1245), col = "IDER model")) + geom_line(aes(x = d_four, y = NTE2_function(d = d_four, L= 195, Z.beta = 1245), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

i_3 = ggplot() + geom_errorbar(data = big_df[49:58, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[49:58], y = big_df$CA[49:58])) + geom_line(aes(x = d_three,  y = 0.00071 + IDER(d = d_three, L = 240, Z.beta = 1585), col = "IDER model")) + geom_line(aes(x = d_three, y = NTE2_function(d = d_three, L = 240, Z.beta = 1585), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank()) + xlim(0, 0.4) + ylim(0, 0.08)

setEPS()
postscript("6_ions.eps", width = 10, height = 7)
grid.arrange(O, S, Ti, i_6, i_4, i_3, ncol = 3)
dev.off()
```

#Continuation for the 6 other panels of NTE2 comparison in Appendix A2 (Not zoomed in version)
```{r, eval = F}
#Comparing our NASA SNTE IDER model with their NTE2 IDER in 16Cacao
O = ggplot() + geom_errorbar(data = big_df[1:9, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[1:9], y = big_df$CA[1:9])) + geom_line(aes(x = d_O,  y = 0.00071 + IDER(d = d_O, L = 75, Z.beta = 595), col = "IDER model")) + geom_line(aes(x = d_O, y = NTE2_function(d = d_O, L= 75, Z.beta = 595), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

S = ggplot() + geom_errorbar(data = big_df[10:20, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[10:20], y = big_df$CA[10:20])) + geom_line(aes(x = d_S,  y = 0.00071 + IDER(d = d_S, L = 100, Z.beta = 690), col = "IDER model")) + geom_line(aes(x = d_S, y = NTE2_function(d = d_S, L= 100, Z.beta = 690), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

Ti = ggplot() + geom_errorbar(data = big_df[21:29, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[21:29], y = big_df$CA[21:29])) + geom_line(aes(x = d_t,  y = 0.00071 + IDER(d = d_t, L = 125, Z.beta = 770), col = "IDER model")) + geom_line(aes(x = d_t, y = NTE2_function(d = d_t, L= 125, Z.beta = 770), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

i_6 = ggplot() + geom_errorbar(data = big_df[30:40, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[30:40], y = big_df$CA[30:40])) + geom_line(aes(x = d_six,  y = 0.00071 + IDER(d = d_six, L = 175, Z.beta = 1075), col = "IDER model")) + geom_line(aes(x = d_six, y = NTE2_function(d = d_six, L= 175, Z.beta = 1075), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

i_4 = ggplot() + geom_errorbar(data = big_df[41:48, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[41:48], y = big_df$CA[41:48])) + geom_line(aes(x = d_four,  y = 0.00071 + IDER(d = d_four, L = 195, Z.beta = 1245), col = "IDER model")) + geom_line(aes(x = d_four, y = NTE2_function(d = d_four, L= 195, Z.beta = 1245), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

i_3 = ggplot() + geom_errorbar(data = big_df[49:58, ], aes(x = d, ymin = errorbar_lower, ymax = errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = big_df$d[49:58], y = big_df$CA[49:58])) + geom_line(aes(x = d_three,  y = 0.00071 + IDER(d = d_three, L = 240, Z.beta = 1585), col = "IDER model")) + geom_line(aes(x = d_three, y = NTE2_function(d = d_three, L = 240, Z.beta = 1585), col = "NTE2 model"), linetype = 2) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank())

setEPS()
postscript("6_ions_2.eps", width = 10, height = 7)
grid.arrange(O, S, Ti, i_6, i_4, i_3, ncol = 3)
dev.off()
```

#Iron and Silicon 2_ion analysis
```{r}
#will create a figure that will do synergy analysis on Silicon and Fe600 and compare it with the simple effect addtivity and the individual IDER curves.
#first panel from d = 0 - 0.1 cGy
d1 = seq(0, 0.001, 0.00001)
out = MIXDER_function(r = c(0.5, 0.5), L = c(100, 175), Z.beta = c(690, 1075), d = d1)
simple_effect = IDER(d = 0.5*d1, L = 100, Z.beta = 690) + IDER(d = 0.5*d1, L = 175, Z.beta = 1075)

g_1_I = out[, 2] + 0.00071
g_1_s =simple_effect + 0.00071
si_IDER = IDER(d = d1, L = 100, Z.beta = 690) + 0.00071
iron_IDER = IDER(d = d1, L = 175, Z.beta = 1075) + 0.00071
figure_one = data.frame(d = d1, g_1_I, g_1_s, si_IDER, iron_IDER)

fig_one = ggplot(data = figure_one) + geom_line(aes(x = d * 100, y = g_1_I * 100), col = "red") + geom_line(aes(x = d * 100, y = g_1_s * 100), col = "black") + labs(x = "", y = "", title = "") + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + geom_line(aes(x = d * 100, y = 100* si_IDER), col = "blue", linetype = "dotted") + geom_line(aes(x = d * 100, y = 100* iron_IDER), col = "blue", linetype = "dotted") 

#second figure from d = 0 - 2
d2 = seq(0, 0.02, 0.0005)
out = MIXDER_function(r = c(0.5, 0.5), L = c(100, 175), Z.beta = c(690, 1075), d = d2)
simple_effect = IDER(d = 0.5*d2, L = 100, Z.beta = 690) + IDER(d = 0.5*d2, L = 175, Z.beta = 1075)

g_1_I = out[, 2] + 0.00071
g_1_s =simple_effect + 0.00071
si_IDER = IDER(d = d2, L = 100, Z.beta = 690) + 0.00071
iron_IDER = IDER(d = d2, L = 175, Z.beta = 1075) + 0.00071
figure_two = data.frame(d = d2, g_1_I, g_1_s, si_IDER, iron_IDER)

fig_two = ggplot(data = figure_two) + geom_line(aes(x = d * 100, y = g_1_I * 100), col = "red") + geom_line(aes(x = d * 100, y = g_1_s * 100), col = "black") + labs(x = "", y = "", title = "") + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + geom_line(aes(x = d * 100, y = 100* si_IDER), col = "blue", linetype = "dotted") + geom_line(aes(x = d * 100, y = 100* iron_IDER), col = "blue", linetype = "dotted")

#third figure from d = 0-500
d3 = c(seq(0, 0.01, 0.0005), seq(0.02, 0.5, 0.01))
out = MIXDER_function(r = c(0.5, 0.5), L = c(100, 175), Z.beta = c(690, 1075), d = d3)
simple_effect = IDER(d = 0.5*d3, L = 100, Z.beta = 690) + IDER(d = 0.5*d3, L = 175, Z.beta = 1075)

g_1_I = out[, 2] + 0.00071
g_1_s =simple_effect + 0.00071
si_IDER = IDER(d = d3, L = 100, Z.beta = 690) + 0.00071
iron_IDER = IDER(d = d3, L = 175, Z.beta = 1075) + 0.00071
figure_three = data.frame(d = d3, g_1_I, g_1_s, si_IDER, iron_IDER)

fig_three = ggplot(data = figure_three) + geom_line(aes(x = d * 100, y = g_1_I * 100), col = "red") + geom_line(aes(x = d * 100, y = g_1_s * 100), col = "black") + labs(x = "", y = "", title = "") + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm")) + geom_line(aes(x = d * 100, y = 100* si_IDER), col = "blue", linetype = "dotted") + geom_line(aes(x = d * 100, y = 100* iron_IDER), col = "blue", linetype = "dotted")

setEPS()
postscript("Fe_Si_2ion.eps", width = 12, height = 4)
grid.arrange(fig_one, fig_two, fig_three, ncol = 3)
dev.off()
#two blue curves are the individual IDER curves, red curve is the MIXDER curve and the black one is the simple effect addtivity curve. We can already see the simple effect overestimating as expected. 
```

#Confidence intervals (CI) and Monte Carlo (MC) simulations 
```{r}
#MonteCarlo using multivariate gaussian 
require(mvtnorm)
sig = vcov(IDER_model)
set.seed(10)
monte_carlo_parameters = rmvnorm(n = 500, mean = c(eta0 = 1.484687e-04, eta1 = 3.513927e-03, sig0 = 4.149660e+00, kap = 4.688287e+02), sigma = sig)
eta0_MC = monte_carlo_parameters[, 1]
eta1_MC = monte_carlo_parameters[, 2]
sig0_MC = monte_carlo_parameters[, 3]
kap_MC = monte_carlo_parameters[, 4]
kap_MC[kap_MC <= 1e-6] = 1e-5 
#note because our last parameter were less significant when inputting our variance covariance matrix the parameters had to actually be readjusted to fix for negative value. This is important because if kap parameter went negative our model is nonsensical. (Luckily the fix was only for exactly 15 out of 500 MC samples or only roughly 3%)

#This is a general CI_function where you just get a CI for a specific dose point for any synergy analysis using the monte carlo simulations using vcov().
CI_function_MIXDER = function(d, d_interested, r, interval = 0.95, L, Z.beta) {
  MIXDER_curve = list(0)
  for (i in 1:500) {
    MIXDER_curve[[i]] = MIXDER_function(r = r, d = d, L = L, Z.beta = Z.beta, eta0 = eta0_MC[i], eta1 = eta1_MC[i], sig0 = sig0_MC[i], kap = kap_MC[i])
  }
  info = vector(length = 0)
  for (i in 1:500) {
    info = c(info, MIXDER_curve[[i]][, 2][2])
  }
  info = sort(info)
  lower_bound = info[(1-interval)/2*500]
  upper_bound = info[(interval + (1-interval)/2)*500]
  CI = c(lower_bound, upper_bound)
  return(CI)
}

#Monte Carlo using the error bars from summary()
set.seed(11)
eta0_MC_2 = rnorm(1000, mean = 1.485e-04, sd = 2.190e-05)
eta1_MC_2 = rnorm(1000, mean = 3.514e-03, sd = 9.037e-04)
sig0_MC_2 = rnorm(1000, mean = 4.150e+00, sd = 1.366e+00)
kap_MC_2 = rnorm(1000, mean = 4.688e+02, sd = 2.469e+02)
kap_MC_2[kap_MC_2 <= 1e-6] = 1e-5 

CI_function_MIXDER_MC_2 = function(d, d_interested, r, interval = 0.95, L, Z.beta) {
  MIXDER_curve = list(0)
  for (i in 1:500) {
    MIXDER_curve[[i]] = MIXDER_function(r = r, d = d, L = L, Z.beta = Z.beta, eta0 = eta0_MC_2[i], eta1 = eta1_MC_2[i], sig0 = sig0_MC_2[i], kap = kap_MC_2[i])
  }
  info = vector(length = 0)
  for (i in 1:500) {
    info = c(info, MIXDER_curve[[i]][, 2][2])
  }
  info = sort(info)
  lower_bound = info[(1-interval)/2*500]
  upper_bound = info[(interval + (1-interval)/2)*500]
  CI = c(lower_bound, upper_bound)
  return(CI)
}
```

#95% CI ribbon for 2_ions
```{r}
#This is for the two_ion ribbon graph. Similarly, blue curves are individual IDERs and red curve the mixed IDER and the black the simple effect addtivity curve

#First the MIXDER of the true curve 
out = MIXDER_function(r = rep(1/2, times = 2), L = c(100, 175), Z.beta = c(690, 1075), d = c(seq(0, 0.01, 0.001), seq(0.01, 0.5, by = 0.01)))
two_ion_MIXDER = data.frame(d = out[, 1], CA = out[, 2] + 0.00071)
d = two_ion_MIXDER$d
#Then the 95% CI multivariate MC simulated ribbon
ninty_five_CI_lower = vector(length = 0)
ninty_five_CI_upper = vector(length = 0)
a = vector(length = 0)
for (i in 2:length(d)) {
  a = CI_function_MIXDER(d = c(0, two_ion_MIXDER$d[i]), d_interested = two_ion_MIXDER$d[i], r = rep(1/2, times = 2),  L = c(100, 175), Z.beta = c(690, 1075))
  ninty_five_CI_lower = c(ninty_five_CI_lower, a[1])
  ninty_five_CI_upper = c(ninty_five_CI_upper, a[2])
}
two_ion_MIXDER$CI_lower = c(0, ninty_five_CI_lower + 0.00071)
two_ion_MIXDER$CI_upper = c(0, ninty_five_CI_upper + 0.00071)

#Get the simple effect additivity MIXDER
two_ion_MIXDER$simpleeffect = IDER(d = 0.5*d, L = 100, Z.beta = 690) + IDER(d = 0.5*d, L = 175, Z.beta = 1075) + 0.00071
#Get the individual IDERS
two_ion_MIXDER$silicon = IDER(d = d, L = 100, Z.beta = 690) + 0.00071
two_ion_MIXDER$ironsix = IDER(d = d, L = 175, Z.beta = 1075) + 0.00071
save(two_ion_MIXDER, file = "two_ion_95%.Rda")

#plotting the 95% ribbon graph for the two_ion MIXDER
fig_44ff_2 = ggplot(data = two_ion_MIXDER, aes(x = d*100, y = CA* 100)) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank()) + geom_ribbon(aes(ymin = CI_lower* 100, ymax = CI_upper * 100), fill = "yellow") + geom_line(aes(y = CA * 100), col = "red", size = 1) + geom_line(aes(y = simpleeffect * 100), col = "black", linetype = "longdash", lwd = 0.5) + geom_line(aes(y = silicon* 100), col = "green", size = 1) + geom_line(aes(y = ironsix* 100), col = "green", size = 1)

setEPS()
postscript("2_ion_MC.eps", width = 6, height = 4)
fig_44ff_2
dev.off()
```

#6 ions analysis using 95% CI ribbons using both methods
```{r}
#This is for the six_ion synergy analysis incorporating our monte carlo simulations with the yellow ribbon as the 95% confidence interval using our monte carlo simulated parameters with two panels for two methods of the MC simulation. Similarly, blues curves are individual IDERs and red curve the mixed IDER and the black the simple effect addtivity curve.

#First the MIXDER of the true curve 
out = MIXDER_function(r = rep(1/6, times = 6), L = c(75, 100, 125, 175, 195, 240), Z.beta = c(595, 690, 770, 1075, 1245, 1585), d = c(seq(0, 0.01, 0.001), seq(0.01, 0.4, by = 0.01)))
six_ion_MIXDER = data.frame(d = out[, 1], CA = out[, 2] + 0.00071)
d = six_ion_MIXDER$d
#Then the 95% CI multivariate MC simulated ribbon
ninty_five_CI_lower = vector(length = 0)
ninty_five_CI_upper = vector(length = 0)
a = vector(length = 0)
for (i in 2:length(d)) {
  a = CI_function_MIXDER(d = c(0, six_ion_MIXDER$d[i]), d_interested = six_ion_MIXDER$d[i], r = rep(1/6, times = 6), L = c(75, 100, 125, 175, 195, 240), Z.beta = c(595, 690, 770, 1075, 1245, 1585))
  ninty_five_CI_lower = c(ninty_five_CI_lower, a[1])
  ninty_five_CI_upper = c(ninty_five_CI_upper, a[2])
}
six_ion_MIXDER$CI_lower = c(0, ninty_five_CI_lower + 0.00071)
six_ion_MIXDER$CI_upper = c(0, ninty_five_CI_upper + 0.00071)

#Then the 95% CI for the MC simulated independent gaussians
ninty_five_CI_lower_two = vector(length = 0)
ninty_five_CI_upper_two = vector(length = 0)
a = vector(length = 0)
for (i in 2:length(d)) {
  a = CI_function_MIXDER_MC_2(d = c(0, six_ion_MIXDER$d[i]), d_interested = six_ion_MIXDER$d[i], r = rep(1/6, times = 6), L = c(75, 100, 125, 175, 195, 240), Z.beta = c(595, 690, 770, 1075, 1245, 1585))
  ninty_five_CI_lower_two = c(ninty_five_CI_lower_two, a[1])
  ninty_five_CI_upper_two = c(ninty_five_CI_upper_two, a[2])
}
six_ion_MIXDER$CI_lower_two = c(0, ninty_five_CI_lower_two + 0.00071)
six_ion_MIXDER$CI_upper_two = c(0, ninty_five_CI_upper_two + 0.00071)

#Get the simple effect additivity MIXDER 
six_ion_MIXDER$simpleeffect = IDER(d = 1/6*d, L = 125, Z.beta = 770) + IDER(d = 1/6*d, L = 175, Z.beta = 1075) + IDER(d = 1/6*d, L = 75, Z.beta = 595) + IDER(d = 1/6*d, L = 100, Z.beta = 690) + IDER(d = 1/6*d, L = 195, Z.beta = 1245) + IDER(d = 1/6*d, L = 240, Z.beta = 1585) + 0.00071
#Get the individual IDERS
six_ion_MIXDER$oxygen = IDER(d = d, L = 75, Z.beta = 595) + 0.00071
six_ion_MIXDER$silicon = IDER(d = d, L = 100, Z.beta = 690) + 0.00071
six_ion_MIXDER$titanium = IDER(d = d, L = 125, Z.beta = 770) + 0.00071
six_ion_MIXDER$ironsix = IDER(d = d, L = 175, Z.beta = 1075) + 0.00071
six_ion_MIXDER$ironfour = IDER(d = d, L = 195, Z.beta = 1245) + 0.00071
six_ion_MIXDER$ironthree = IDER(d = d, L = 240, Z.beta = 1585) + 0.00071
save(six_ion_MIXDER, file = "six_ion_95%.Rda")

#plotting first panel for MC multivariate gaussian using vcov()
fig_42ff_1 = ggplot(data = six_ion_MIXDER, aes(x = d*100, y = CA* 100)) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank()) + geom_ribbon(aes(ymin = CI_lower* 100, ymax = CI_upper * 100), fill = "yellow") + geom_line(aes(y = CA * 100), col = "red", size = 1) + geom_line(aes(y = simpleeffect * 100), col = "black", linetype = "longdash", lwd = 0.5) + geom_line(aes(y = silicon* 100), col = "green", size = 1) + geom_line(aes(y = titanium* 100), col = "green", size = 1) + geom_line(aes(y = ironthree* 100), col = "green", size = 1) + geom_line(aes(y = ironfour* 100, size = 1), col = "green", size = 1) + geom_line(aes(y = ironsix* 100), col = "green", size = 1) + geom_line(aes(y = oxygen* 100), col = "green", size = 1) 

#Plotting second figure independent gaussian using summary() instead of vcov()
fig_42ff_2 = ggplot(data = six_ion_MIXDER, aes(x = d*100, y = CA* 100)) + labs(x = "", y = "", title = "") + scale_colour_manual(guide = FALSE, name = "Models", values = c("red", "blue"), label = c("IDER", "NTE1")) + theme_bw() + theme(axis.line.x = element_line(color="black", size = 0.3), axis.line.y = element_line(color="black", size = 0.3), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.ticks.y = element_line(size = 0.3), axis.ticks.x = element_line(size = 0.3), axis.text=element_text(size=12), axis.title=element_text(size=14), axis.ticks.length = unit(0.3, "cm"), axis.text.x = element_blank(), axis.text.y = element_blank(), panel.border = element_blank()) + geom_ribbon(aes(ymin = CI_lower_two* 100, ymax = CI_upper_two * 100), fill = "yellow") + geom_line(aes(y = CA * 100), col = "red", size = 1) + geom_line(aes(y = simpleeffect * 100), col = "black", linetype = "longdash", lwd = 0.5) + geom_line(aes(y = silicon* 100), col = "green", size = 1) + geom_line(aes(y = titanium* 100), col = "green", size = 1) + geom_line(aes(y = ironthree* 100), col = "green", size = 1) + geom_line(aes(y = ironfour* 100, size = 1), col = "green", size = 1) + geom_line(aes(y = ironsix* 100), col = "green", size = 1) + geom_line(aes(y = oxygen* 100), col = "green", size = 1) 

setEPS()
postscript("6_ion_MC.eps", width = 12, height = 4)
grid.arrange(fig_42ff_1, fig_42ff_2, ncol = 2)
dev.off()
```