# This is free, open-source software under the (lenient) GNU GPLv3. It comes with no warranty. 
# Written by Dae Woong Ham between Sept. 2016 and May 2017. Some quality control by Rainer (Ray) K. Sachs (rks) May-August 2017.
# This version written by Liyang (Andy) Zhao (laz) UCB academic year 2017-2018. Some quality control by rks and Julien Yu.
# Script concerns synergy analysis of WGE simple chromosome aberrations (CA) induced in 82-6 fibroblast cells by simulated GCR (Galactic Cosmic Radiation) mixed fields.
#The script uses various mixture component one-ion DERs (Dose Effect Relations), summarized in "16Cacao" = 
# = Cacao, Hada, Saganti, George and Cucinotta. "Relative Biological Effectiveness of HZE Particles for Chromosomal Exchanges and Other Surrogate Cancer Risk Endpoints." PLoS One 11(4): e0153998. (2016)].
#The libraries needed for this script
```{r}
library(deSolve) # package for solving differential equations
library(minpack.lm) # package for non-linear regression #rks to laz: I think we probably can just use nls() in stats, not nlsLM from linpack. Please check in R documentation if there is any functional difference at all
library(mvtnorm) # package for calculating confidence intervals by Monte Carlo simulation based on variance-covariance matrices #rks to laz: I added to comment.Please check that my addition is OK.
rm(list=ls())
```

#Data
##16Cacao data
```{r}
#Create dataframes that store the fibroblast WGE simple CA data used in 16Cacao 

Oxygen = data.frame(d = c(0, .0125, .02, .025, .05, .075, .1, .2, .4),CA = c(.24, 1.66, 2.43, 2.37, 1.16, 2.85, 2.58, 6.94, 6.91), ion = "O", Z =8, L = 75, Z.b = 795)
# Some GCR components are high-speed Oxygen nuclei that are almost fully ionized. d=dose; CA are per hundred cells.

Si = data.frame(d = c(0, .02, .04, .06, .08, .1, .12, .2, .4, .8, 1.2), CA = c(.11, 1.26, 1.14, 1.58, 1.22, 1.89, 3.47, 4.6, 9.79, 27.01, 38.84), ion = "Si", Z = 14, L = 100, Z.b = 690)

Fe600 = data.frame(d = c(0, .01, .02, .04, .06, .08, .1, .12, .2, .4, .8), CA = c(.13, .76, .99, 1.2, 1.74, 1.28, 1.2, 1.7, 3.02, 5.52, 12.42), ion = "Fe600", Z = 26, L = 175, Z.b = 1075) 
#600 refers to the energy in MeV per atomic mass unit in this Iron beam

Fe450 = data.frame(d = c(0, .02, .04, .06, .08, .1, .2, .4), CA = c(0, .86, .6, .8, 1.22, 2.02, 2.3, 4.77), ion = "Fe450", Z = 26, L = 195, Z.b = 1245)

Fe300 = data.frame(d = c(0, .005, .01,  0.02, .04, .07, .1, .2, .4, .8), CA = c(0.41, 1.23, 1.47, 1.22, .97, 1.46, 1.21, 4.38, 6.22, 13.6), ion = "Fe300", Z = 26, L = 240, Z.b = 1585)

Ti = data.frame(d = c(0,  0.02, .04, .06, .08, .1, .15, .3, .6), CA = c(0, 1.99, 1.88, 1.44, 2.67, 2.57, 2.50, 5.64, 11.19), ion = "Ti", Z = 22, L = 125, Z.b = 770)

#param = data.frame(ion = c("O", "Si", "Ti", "Fe600", "Fe450", "Fe300"),
                  # Z = c(8, 14, 22, 26, 26, 26), L = c(75, 100, 125, 175, 195, 240), #Z=atomic charge; L=LET
                  # Z.b = c(595, 690, 770, 1075, 1245, 1585))#Z^2/beta*^2

#putting it in one big data frame. #rks: the data frame incorporates a correction to Fe600 at dose 0.06, near line 34
big_df = rbind(Oxygen, Si, Ti, Fe600, Fe450, Fe300)

big_df$error = c(0.24, 0.63, 0.77, 0.75, 0.52, 0.82, 0.78, 1.31, 1.59, 0.12, 0.05, 0.07, 0.56, 0.18, 0.60, 1.23, 1.60, 1.55, 4.27, 7.21, 0, 0.70, 0.66, 0.59, 0.80, 0.78, 0.48, 1.15, 2.39, 0.16, 0.38, 0.24, 0.21, 0.43, 0.37, 0.54, 0.17, 0.55, 1.75, 2.59, 0, 0.43, 0.34, 0.40, 0.50, 0.64, 0.73, 1.09, 0.29, 0.55, 0.60, 0.55, 0.49, 0.60, 0.54, 1.03, 1.22, 3.62) #error bars for the CA measurements
```

```{r}
#Next modify the data frame to get rid of the zero dose points. Background CA frequency was determined seperately.
modified_df = big_df[big_df$d != 0, ]
modified_df$CA = modified_df$CA*0.01 
modified_df$error = modified_df$error*0.01
big_df$CA = big_df$CA * 0.01
big_df$error = big_df$error * 0.01
big_df$errorbar_lower = big_df$CA - big_df$error
big_df$errorbar_upper = big_df$CA + big_df$error
```

#Calibrating parameters and Model Selection
##Three models: NTE1, NTE2 and IDER
```{r}
#NTE1 and NTE2 models in 16Cacao using their parameters. NTE is used in 16Cacao to signify that non-targeted effects are included in the model; Conventional targeted effects (TE) are included in all models.
#NTE1 function
NTE1_function = function(d, L, Z.b, eta0 = 0.00011, eta1 = 0.007, sig0 = 6.12, kap = 796) {
  0.0017 + eta0*L*exp(-eta1*L)*(d != 0) + 
    (6.242*(d/L))*(sig0*(1-exp(-Z.b/kap))^2 + 0.041/6.24*L*(1 - (1-exp(-Z.b/kap))^2))
} 

#NTE2 function
NTE2_function = function(d, L, Z.b, eta0 = 0.00047, eta1 = 0.011, sig0 = 6.75, kap = 590) {
  0.0017 + eta0*L*exp(-eta1*L)*exp(-(1012*(d/L)))*(d != 0) + 
    (6.242*(d/L))*(1-exp(-(1012*(d/L))))*
    (sig0*(1-exp(-Z.b/kap))^2 + 0.041/6.24*L*(1 - (1-exp(-Z.b/kap))^2))
}

#Our IDERs (Individual Dose Effect Relations). Applicable to the 1-ion components of a mixed simulated GCR beam 
#Modifying NTE1 and NTE2 by insisting they be twice continuously differentiable and monotonic increasing. Double check NTE1, NTE2, Our model
IDER = function(d, L, Z.b, eta00, eta10, sig00, kap0) {
  P = (1-exp(-Z.b/kap0))^2
  sig = sig00*P + 0.041/6.24*L*(1-P) # 0.041 +- 0.0051 comes from 16Cacao
  eta = eta00*L*exp(-eta10*L)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))  #0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^3*d))#don't use
} 

#nls (non-linear least square) method to get the parameters needed (4 parameter estimation) #rks to laz: see note under issues
IDER_model = nlsLM(CA ~ IDER(d, L, Z.b, eta00, eta10, sig00, kap0), data = modified_df, start = list(eta00 = 0.001, eta10 = 0.01, sig00 = 5, kap0 = 500), 
                   weights = (1/(modified_df$error)^2))
coef(IDER_model)
#e.g. eta0 = 1.484687e-04, eta1 = 3.513927e-03, sig0 = 4.149660e+00, kap = 4.688287e+02
vcov(IDER_model)# variance-covariance matrix, needed later for analyzing 95% confidence limits in baseline no-synergy/no-antagonism MIXDER (Mixture dose effect relation)
summary(IDER_model, cor = TRUE) #model parameters and their correlation matrix
```

```{r}
#Getting coefficients of the IDER model from nlsLM
coefs <- coef(IDER_model)
eta0_hat <- as.numeric(coefs[1])
eta1_hat <- as.numeric(coefs[2])
sig0_hat <- as.numeric(coefs[3])
kap_hat <- as.numeric(coefs[4])
```

##Model Selection using AIC/BIC of the WRSS
```{r}
#R function to give Information criteria (AIC and BIC) #rks to laz: R has AIC functions. Please check that they give the same ordering (not necessarily the same values) as the ones constructed below by Dae or you.
#L_function gives the residuals squared
L_function = function(func, eta0, eta1, sig0, kap) {
  a = vector(length = 0)
  for (i in 1:length(modified_df[, 1])) {
    a = c(a, modified_df$CA[i] - func(d = modified_df$d[i], L = modified_df$L[i], Z.b = modified_df$Z.b[i], eta0 = eta0, eta1 = eta1, sig0 = sig0, kap = kap))
  }
  return(a^2)
}
L_NTE1 = L_function(NTE1_function, eta0 = 0.00011, eta1 = 0.007, sig0 = 6.12, kap = 796)
L_NTE2 = L_function(NTE2_function, eta0 = 0.00047, eta1 = 0.011, sig0 = 6.75, kap = 590)
L_IDER = L_function(IDER, eta0 = eta0_hat, eta1 = eta1_hat, sig0 = sig0_hat, kap = kap_hat)

#Since all models are weighted least square regression, will weight our model with our weights to get the WRSS (weighted residual squared sum)
WRSS_NTE1 = sum((1/modified_df$error^2)*L_NTE1)
WRSS_NTE2 = sum((1/modified_df$error^2)*L_NTE2)
WRSS_IDER = sum((1/modified_df$error^2)*L_IDER)

#functions for AIC and BIC calculation for Weighted Least Square regression
AIC_function = function(RSS, k = 4, n = length(modified_df[ , 1])) {
  n + n*log(2*pi) + n*log(RSS/n) + 2*(k+1)
}

BIC_function = function(n = length(modified_df[, 1]), k = 4, RSS) {
  n + n*log(2*pi) + n*log(RSS/n) + log(n)*(k+1)
}

NTE1_AIC = AIC_function(RSS = WRSS_NTE1)
NTE2_AIC = AIC_function(RSS = WRSS_NTE2)
IDER_AIC = AIC_function(RSS = WRSS_IDER)
NTE1_BIC = BIC_function(RSS = WRSS_NTE1)
NTE2_BIC = BIC_function(RSS = WRSS_NTE2)
IDER_BIC = BIC_function(RSS = WRSS_IDER)
information_critera_df = data.frame(AIC = c(NTE1_AIC, NTE2_AIC, IDER_AIC), BIC = c(NTE1_BIC, NTE2_BIC, IDER_BIC), row.names = c("NTE1 model", "NTE2 model", "IDER model"))
information_critera_df ## RKS runs well up to here. Lots of checks made 8/12/2017
```

##MIXDER_function and graph
```{r}
#Baseline no-synergy/no-antagonism MIXDER  based on any input
MIXDER_function = function(r, L, Z.b, d = seq(0, 0.2, by = 0.001), eta0 = eta0_hat, eta1 = eta1_hat, sig0 = sig0_hat ,kap = kap_hat) {
  dE=function(yini,State,Pars){
    eta0 = eta0; eta1 = eta1; sig0 = sig0; kap = kap
    with(as.list(c(State, Pars)), {
      P = vector(length = length(L))
      sig = vector(length = length(L))
      etaa = vector(length = length(L))
      u = vector(length = length(L))
      for (i in 1:length(L)) {
        P[i] = (1-exp(-Z.b[i]/kap))^2
        sig[i] = sig0*P[i] + 0.041/6.24*L[i]*(1-P[i])
        etaa[i] = eta0*L[i]*exp(-eta1*L[i])
        u[i] = uniroot(function(d) sig[i]*6.24*d/L[i]*(1-exp(-1024*d/L[i])) + etaa[i]*(1-exp(-10^5*d)) - I, lower = 0, upper = 1, extendInt = "yes", tol = 10^-10)$root
      }
      dI = vector(length = length(L))
      for (i in 1:length(L)) {
        dI[i] = r[i]*(sig[i]*6.24/L[i]*exp(-1024*u[i]/L[i])*(exp(1024*u[i]/L[i]) + 1024*u[i]/L[i] - 1) + etaa[i]*10^5*exp(-10^5*u[i]))
      }
      dI = sum(dI)
      return(list(c(dI)))
    })
  }
  pars = NULL; yini = c(I= 0); d = d
  out = ode(yini,times = d, dE, pars, method = "radau")
  return(out)
}

```

```{r}
#Graphs for NTE1 and our IDER models: 12_ion figure
#When creating any sort of MIXDER figures we use this IDER now without the background effect then add the background effect at the end.
IDER = function(d, L, Z.b, eta0 = eta0_hat, eta1 = eta1_hat, sig0 = sig0_hat, kap = kap_hat) {
  P = (1-exp(-Z.b/kap_hat))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  eta = eta0*L*exp(-eta1*L)
  sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))#sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-.5*10^3*d))#don't use
} 

#Simple Effect Additivity (black line)
SEA=function(d){
  IDER(d/6,L[1],Z.b[1])+IDER(d/6,L[2],Z.b[2])+IDER(d/6,L[3],Z.b[3])+IDER(d/6,L[4],Z.b[4])+IDER(d/6,L[5],Z.b[5])+IDER(d/6,L[6],Z.b[6])
}

r=rep(1/6,6);L = c(75, 100, 125, 175, 195, 240); Z.b = c(595, 690, 770, 1075, 1245, 1585); dose=seq(0, 0.4, by=0.001)

MX=MIXDER_function(r, L, Z.b, d=dose) #for this mixture can't go much above 0.6#

#Plotting
plot(MX[,1],MX[,2],type='l',bty='l',col='red',ann='F',ylim=c(0,.10), main="CA vs Dose", xlab="Dose", ylab="CA")
for (ii in 1:length(L)){lines(dose, IDER(dose,L[ii],Z.b[ii]),col='green')}
lines(dose,SEA(dose),lty=2)
```

```{r}
#lines(dose,sum(SEA))
#Comparing the NTE1 model in 16Cacao with our NASA SNTE model

#Use these dose points to generate the curves necessary. Had to include a lot more dose points at lower doses where it is very sensitive to change
# d_O = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:40))
# d_1 = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:9), 1e-2*(1:9), 0.01*(10:15))
# d_2 = c(0, 1e-6*(1:9), 1e-5*(1:9), 1e-4*(1:9), 1e-3*(1:300))
# plot(c(0,.3),c(0,0.04), bty='l', ann='F')
# lines(d_2,IDER(d_2,240,1585), bty='l', ann='F')
# #setEPS()
# postscript("NTE1_model test.eps", width = 5, height = 7)
# par(mfrow=c(2,1))
# 
# plot(x = big_df$d[1:9]*100, y = big_df$CA[1:9]*100, main = "Oxygen", ylim = c(0, 10),pch=19, ylab = "CA", xlab = "Dose (cGy)")
# arrows(big_df$d[1:9]*100, big_df$errorbar_lower[1:9]*100, big_df$d[1:9]*100, big_df$errorbar_upper[1:9]*100, length=0.02, angle=90, code=3)
# lines(x = d_O*100, y = 100*(0.00071 + IDER(d = d_O, L = 75, Z.b = 595)), col = "red")
# lines(x = d_O*100, y = 100 * NTE1_function(d = d_O, L= 75, Z.b = 595), col = "blue", lty = 2)
# 
# plot(x = big_df$d[1:7]*100, y = big_df$CA[1:7]*100, main = "Oxygen",pch=19, ylab = "CA", xlab = "Dose (cGy)", ylim = c(0, 4), xlim = c(0, 15))
# arrows(big_df$d[1:7]*100, big_df$errorbar_lower[1:7]*100, big_df$d[1:7]*100, big_df$errorbar_upper[1:7]*100, length=0.02, angle=90, code=3)
# lines(x = d_1*100, y = 100*(0.00071 + IDER(d = d_1, L = 75, Z.b = 595)), col = "red")
# lines(x = d_1*100, y = 100 * NTE1_function(d = d_1, L= 75, Z.b = 595), col = "blue", lty = 2)
# 
# dev.off()
```

#Confidence Intervals
##Sample parameters from normal distributions (with and without covariances)
```{r}
set.seed(19970101)
MM <- 500
```

```{r}
#Sample parameters from their distributions with covariances
sig = vcov(IDER_model)
monte_carlo_parameters = rmvnorm(n = MM, mean = c(eta0 = eta0_hat, eta1 = eta1_hat, sig0 = sig0_hat, kap = kap_hat), sigma = sig)
eta0_MC = monte_carlo_parameters[, 1]
eta1_MC = monte_carlo_parameters[, 2]
sig0_MC = monte_carlo_parameters[, 3]
kap_MC = monte_carlo_parameters[, 4]
kap_MC[kap_MC <= 1e-6] = 1e-5 #10 of them were fixed

#Sample parameters from their distributions without covariances
eta0_MC_var = rnorm(MM, mean = eta0_hat, sd = 4.631e-05)
eta1_MC_var = rnorm(MM, mean = eta1_hat, sd = 1.617e-04)
sig0_MC_var = rnorm(MM, mean = sig0_hat, sd = 1.966e+00)
kap_MC_var = rnorm(MM, mean = kap_hat, sd = 2.628e+02)
kap_MC_var[kap_MC_var <= 1e-6] = 1e-5 

#note because our last parameter were less significant when inputting our variance covariance matrix the parameters had to actually be readjusted to fix for negative value. This is important because if kap parameter went negative our model is nonsensical. (Luckily the fix was only for exactly 10 out of 500 MC samples or only 2%)

```

##Monte Carlo functions (without and with covariance)
```{r}
#This is a general CI_function where you just get a CI for a specific dose point for any synergy analysis using the monte carlo simulations using vcov().
CI_function_MIXDER = function(d, r, interval = 0.95, L, Z.beta) {
  MIXDER_curve = list(0)
  for (i in 1:MM) {
    MIXDER_curve[[i]] = MIXDER_function(r = r, d = d, L = L, Z.b = Z.b, eta0 = eta0_MC[i], eta1 = eta1_MC[i], sig0 = sig0_MC[i], kap = kap_MC[i])
  }
  info = vector(length = 0)
  for (i in 1:MM) {
    info = c(info, MIXDER_curve[[i]][, 2][2])
  }
  info = sort(info)
  lower_bound = quantile(info,(1-interval)/2)
  upper_bound = quantile(info,1-(1-interval)/2)
  CI = c(lower_bound, upper_bound)
  return(CI)
}
# We don't actually need the above CI_Function_MIXDER (there was an error for some reason) #pw: I will fix this error eventually. Right now we are still using the for loop Andy created.
```

```{r}
#This is the same function as above except that it is using parameters WITHOUT covariance matrix.
CI_function_MIXDER_var = function(d, d_interested, r, interval = 0.95, L, Z.beta) {
  MIXDER_curve = list(0)
  for (i in 1:MM) {
    MIXDER_curve[[i]] = MIXDER_function(r = r, d = d, L = L, Z.b = Z.b, eta0 = eta0_MC_var[i], eta1 = eta1_MC_var[i], sig0 = sig0_MC_var[i], kap = kap_MC_var[i])
  }
  info = vector(length = 0)
  for (i in 1:MM) {
    info = c(info, MIXDER_curve[[i]][, 2][2])
  }
  info = sort(info)
  lower_bound = info[(1-interval)/2*MM]
  upper_bound = info[(interval + (1-interval)/2)*MM]
  CI = c(lower_bound, upper_bound)
  return(CI)
}
```

##2-ion CI's
###2-ion 60 doses
```{r}
#MIXDER of iron 2.
d1 = c(seq(0, 0.009, 0.001), seq(0.01, 0.5, by = 0.01))
out = MIXDER_function(r = rep(1/2, times = 2), L = c(100, 175), Z.b = c(690, 1075), d = d1, eta0 = eta0_hat, eta1 = eta1_hat, sig0 = sig0_hat, kap = kap_hat)
two_ion_MIXDER = data.frame(d = out[, 1], CA = out[, 2] + 0.00071)
```

```{r}
# Monte Carlo of using 60 doses for two_ion. 
ninty_five_CI_lower = vector(length = length(d1))
ninty_five_CI_upper = vector(length = length(d1))
for (i in 1:length(d1)){
  info = vector(length = 0)
  for (j in 1:MM){
    info = c(info, MIXDER_function(r = rep(1/2, times = 2), c(0, two_ion_MIXDER$d[i]),L=c(100, 175), Z.b = c(690, 1075), eta0 = eta0_MC[j], eta1 = eta1_MC[j], sig0 = sig0_MC[j], kap = kap_MC[j])[,2][2])
  }
  info = sort(info)
  ninty_five_CI_lower[i] = quantile(info,(1-0.95)/2) + 0.00071
  ninty_five_CI_upper[i] = quantile(info,1-(1-0.95)/2) + 0.00071
}
two_ion_MIXDER$CI_lower = ninty_five_CI_lower
two_ion_MIXDER$CI_upper = ninty_five_CI_upper
```

```{r}
#Get the simple effect additivity MIXDER
two_ion_MIXDER$simpleeffect = IDER(d = 0.5*d1, L = 100, Z.b = 690) + IDER(d = 0.5*d1, L = 175, Z.b = 1075) + 0.00071
#Get the individual IDERS
two_ion_MIXDER$silicon = IDER(d = d1, L = 100, Z.b = 690) + 0.00071
two_ion_MIXDER$ironsix = IDER(d = d1, L = 175, Z.b = 1075) + 0.00071

#The graphing part
d1 <- two_ion_MIXDER$d
CA1 <- two_ion_MIXDER$CA
simpleeffect1 <- two_ion_MIXDER$simpleeffect
silicon1 <- two_ion_MIXDER$silicon
ironsix1 <- two_ion_MIXDER$ironsix
plot(x = d1 * 100, y = CA1 * 100, type = "l", col = "red")
lines(x = d1 * 100, y = simpleeffect1 * 100, col = "black", lty = 2, lwd = 0.5)
lines(x = d1 * 100, y = silicon1* 100, col = "green")  
lines(x = d1 * 100, y = ironsix1* 100, col = "green")
lines(x= d1*100 , y = two_ion_MIXDER$CI_upper * 100, lty = 'dashed', col = 'red')
lines(x= d1*100 , y = two_ion_MIXDER$CI_lower * 100, lty = 'dashed', col = 'red')
polygon(c(d1*100,rev(d1*100)),c(two_ion_MIXDER$CI_lower * 100, rev(two_ion_MIXDER$CI_upper * 100)),col = rgb(1, 0, 0,0.5), border = NA)
```

###2-ion 12 doses (For runtime purpose only)
```{r}
two_ion_MIXDER_small <- two_ion_MIXDER[seq(1,60, by = 5), ]

#The graphing part
d2 <- two_ion_MIXDER_small$d
CA2 <- two_ion_MIXDER_small$CA
simpleeffect2 <- two_ion_MIXDER_small$simpleeffect
silicon2 <- two_ion_MIXDER_small$silicon
ironsix2 <- two_ion_MIXDER_small$ironsix
plot(x = d2 * 100, y = CA2 * 100, type = "l", col = "red", main="2-ion Model", sub="12 Doses", 
     xlab="Dose * 100", ylab="CA * 100")
lines(x = d2 * 100, y = simpleeffect2 * 100, col = "black", lty = 2, lwd = 0.5)
lines(x = d2 * 100, y = silicon2* 100, col = "green")  
lines(x = d2 * 100, y = ironsix2* 100, col = "green")
lines(x= d2*100 , y = two_ion_MIXDER_small$CI_upper * 100, lty = 'dashed', col = 'red')
lines(x= d2*100 , y = two_ion_MIXDER_small$CI_lower * 100, lty = 'dashed', col = 'red')
polygon(c(d2*100,rev(d2*100)),c(two_ion_MIXDER_small$CI_lower * 100, rev(two_ion_MIXDER_small$CI_upper * 100)),col = rgb(1, 0, 0,0.5), border = NA)
```

###2-ion 60 doses without covariance
```{r}
two_ion_MIXDER_var = data.frame(d = out[, 1], CA = out[, 2] + 0.00071)
# Confidence Interval for two-ion without variance and covariance matrix.
ninty_five_CI_lower = vector(length = 0)
ninty_five_CI_upper = vector(length = 0)
a = vector(length = 0)
for (i in 2:length(d1)) {
  print(d1[i])
  a = CI_function_MIXDER_var(d = c(0, two_ion_MIXDER_var$d[i]), r = rep(1/2, times = 2), L=c(100, 175), Z.b = c(690, 1075))
  ninty_five_CI_lower = c(ninty_five_CI_lower, a[1])
  ninty_five_CI_upper = c(ninty_five_CI_upper, a[2])
}
two_ion_MIXDER_var$CI_lower = c(0, ninty_five_CI_lower) + 0.00071
two_ion_MIXDER_var$CI_upper = c(0, ninty_five_CI_upper) + 0.00071

#Get the simple effect additivity MIXDER
two_ion_MIXDER_var$simpleeffect = IDER(d = 0.5*d1, L = 100, Z.b = 690) + IDER(d = 0.5*d1, L = 175, Z.b = 1075) + 0.00071
#Get the individual IDERS
two_ion_MIXDER_var$silicon = IDER(d = d1, L = 100, Z.b = 690) + 0.00071
two_ion_MIXDER_var$ironsix = IDER(d = d1, L = 175, Z.b = 1075) + 0.00071

d1 <- two_ion_MIXDER_var$d
CA1 <- two_ion_MIXDER_var$CA
simpleeffect1 <- two_ion_MIXDER_var$simpleeffect
silicon1 <- two_ion_MIXDER_var$silicon
ironsix1 <- two_ion_MIXDER_var$ironsix
plot(x = d1 * 100, y = CA1 * 100, type = "l", col = "red")
lines(x = d1 * 100, y = simpleeffect1 * 100, col = "black", lty = 2, lwd = 0.5)
lines(x = d1 * 100, y = silicon1* 100, col = "green")  
lines(x = d1 * 100, y = ironsix1* 100, col = "green")
lines(x= d1*100 , y = two_ion_MIXDER_var$CI_upper * 100, lty = 'dashed', col = 'red')
lines(x= d1*100 , y = two_ion_MIXDER_var$CI_lower * 100, lty = 'dashed', col = 'red')
polygon(c(d1*100,rev(d1*100)),c(two_ion_MIXDER_var$CI_lower * 100, rev(two_ion_MIXDER_var$CI_upper * 100)),col = rgb(1, 0, 0,0.5), border = NA)

#write.csv(two_ion_MIXDER_var, "2ionMonteCarlovar.csv", row.names = F)
```


##6-ion CI's
###6-ion 50 doses
```{r}
#This is for the six_ion synergy analysis incorporating our monte carlo simulations with the yellow ribbon as the 95% confidence interval using our monte carlo simulated parameters with two panels for two methods of the MC simulation. Similarly, blues curves are individual IDERs and red curve the mixed IDER and the black the simple effect addtivity curve.

#First the MIXDER of the true curve 
d3 = c(seq(0, 0.009, 0.001), seq(0.01, 0.4, by = 0.01))
out = MIXDER_function(r = rep(1/6, times = 6), L = c(75, 100, 125, 175, 195, 240), Z.b = c(595, 690, 770, 1075, 1245, 1585), d = c(seq(0, 0.009, 0.001), seq(0.01, 0.4, by = 0.01)))
six_ion_MIXDER = data.frame(d = out[, 1], CA = out[, 2] + 0.00071)

#six_ion_MIXDER = data.frame(d = out[, 1], CA = out[, 2] + 0.00071)  #This is the full 50 dose version.
#d3 = six_ion_MIXDER3$d

```

```{r}
#Then the 95% CI multivariate MC simulated ribbon for 11 doses.
ninty_five_CI_lower = vector(length = length(d3))
ninty_five_CI_upper = vector(length = length(d3))
for (i in 1:length(d3)){
  info = vector(length = 0)
  for (j in 1:MM){
    info = c(info, MIXDER_function(r = rep(1/6, times = 6), c(0,  six_ion_MIXDER$d[i]),L = c(75, 100, 125, 175, 195, 240), Z.b = c(595, 690, 770, 1075, 1245, 1585), eta0 = eta0_MC[j], eta1 = eta1_MC[j], sig0 = sig0_MC[j], kap = kap_MC[j])[,2][2])
  }
  info = sort(info)
  ninty_five_CI_lower[i] = quantile(info,(1-0.95)/2) + 0.00071
  ninty_five_CI_upper[i] = quantile(info,1-(1-0.95)/2) + 0.00071
}
six_ion_MIXDER$CI_lower = ninty_five_CI_lower
six_ion_MIXDER$CI_upper = ninty_five_CI_upper
```
```{r}
#Get the simple effect additivity MIXDER 
six_ion_MIXDER$simpleeffect = IDER(d = 1/6*d3, L = 125, Z.b = 770) + IDER(d = 1/6*d3, L = 175, Z.b = 1075) + IDER(d = 1/6*d3, L = 75, Z.b = 595) + IDER(d = 1/6*d3, L = 100, Z.b = 690) + IDER(d = 1/6*d3, L = 195, Z.b = 1245) + IDER(d = 1/6*d3, L = 240, Z.b = 1585) + 0.00071

#Get the individual IDERS
six_ion_MIXDER$oxygen = IDER(d = d3, L = 75, Z.b = 595) + 0.00071
six_ion_MIXDER$silicon = IDER(d = d3, L = 100, Z.b = 690) + 0.00071
six_ion_MIXDER$titanium = IDER(d = d3, L = 125, Z.b = 770) + 0.00071
six_ion_MIXDER$ironsix = IDER(d = d3, L = 175, Z.b = 1075) + 0.00071
six_ion_MIXDER$ironfour = IDER(d = d3, L = 195, Z.b = 1245) + 0.00071
six_ion_MIXDER$ironthree = IDER(d = d3, L = 240, Z.b = 1585) + 0.00071

#The graphing part
d3 <- six_ion_MIXDER$d
CA3 <- six_ion_MIXDER$CA
simpleeffect3 <- six_ion_MIXDER$simpleeffect
silicon3 <- six_ion_MIXDER$silicon
titanium3 <- six_ion_MIXDER$titanium
ironthree3 <- six_ion_MIXDER$ironthree
ironfour3 <- six_ion_MIXDER$ironfour
ironsix3 <- six_ion_MIXDER$ironsix
oxygen3 <- six_ion_MIXDER$oxygen
plot(x = d3 * 100, y = CA3 * 100, type = "l", col = "red")
lines(x = d3 * 100, y = simpleeffect3 * 100, col = "black", lty = 2, lwd = 0.5)
lines(x = d3 * 100, y = silicon3* 100, col = "green")  
lines(x = d3 * 100, y = titanium3* 100, col = "green")
lines(x = d3 * 100, y = ironthree3* 100, col = "green")  
lines(x = d3 * 100, y = ironfour3* 100, col = "green")
lines(x = d3 * 100, y = ironsix3* 100, col = "green")  
lines(x = d3 * 100, y = oxygen3* 100, col = "green")
lines(x= d3*100 , y = six_ion_MIXDER$CI_upper * 100, lty = 'dashed', col = 'red')
lines(x= d3*100 , y = six_ion_MIXDER$CI_lower * 100, lty = 'dashed', col = 'red')
polygon(c(d3*100,rev(d3*100)),c(six_ion_MIXDER$CI_lower * 100, rev(six_ion_MIXDER$CI_upper * 100)),col = rgb(1, 0, 0,0.5), border = NA)
```

###6-ion 10 doses (For runtime purpose only)
```{r}
#Get the simple effect additivity MIXDER 
six_ion_MIXDER_small <- six_ion_MIXDER[seq(1, 50, by = 5),]

#The graphing part
d4 <- six_ion_MIXDER_small$d
CA4 <- six_ion_MIXDER_small$CA
simpleeffect4 <- six_ion_MIXDER_small$simpleeffect
silicon4 <- six_ion_MIXDER_small$silicon
titanium4 <- six_ion_MIXDER_small$titanium
ironthree4 <- six_ion_MIXDER_small$ironthree
ironfour4 <- six_ion_MIXDER_small$ironfour
ironsix4 <- six_ion_MIXDER_small$ironsix
oxygen4 <- six_ion_MIXDER_small$oxygen
plot(x = d4 * 100, y = CA4 * 100, type = "l", col = "red")
lines(x = d4 * 100, y = simpleeffect4 * 100, col = "black", lty = 2, lwd = 0.5)
lines(x = d4 * 100, y = silicon4* 100, col = "green")  
lines(x = d4 * 100, y = titanium4* 100, col = "green")
lines(x = d4 * 100, y = ironthree4* 100, col = "green")  
lines(x = d4 * 100, y = ironfour4* 100, col = "green")
lines(x = d4 * 100, y = ironsix4* 100, col = "green")  
lines(x = d4 * 100, y = oxygen4* 100, col = "green")
lines(x= d4*100 , y = six_ion_MIXDER_small$CI_upper * 100, lty = 'dashed', col = 'red')
lines(x= d4*100 , y = six_ion_MIXDER_small$CI_lower * 100, lty = 'dashed', col = 'red')
polygon(c(d4*100,rev(d4*100)),c(six_ion_MIXDER_small$CI_lower * 100, rev(six_ion_MIXDER_small$CI_upper * 100)),col = rgb(1, 0, 0,0.5), border = NA)
```

###6-ion 50 doses without covariance
```{r}
#6-ion No Covariance 50 dose
CI_function_MIXDER_var = function(d, d_interested, r, interval = 0.95, L, Z.beta) {
  MIXDER_curve = list(0)
  for (i in 1:MM) {
    MIXDER_curve[[i]] = MIXDER_function(r = r, d = d, L = L, Z.b = Z.b, eta0 = eta0_MC_var[i], eta1 = eta1_MC_var[i], sig0 = sig0_MC_var[i], kap = kap_MC_var[i])
  }
  info = vector(length = 0)
  for (i in 1:MM) {
    info = c(info, MIXDER_curve[[i]][, 2][2])
  }
  info = sort(info)
  lower_bound = info[(1-interval)/2*MM]
  upper_bound = info[(interval + (1-interval)/2)*MM]
  CI = c(lower_bound, upper_bound)
  return(CI)
}
six_ion_MIXDER_var = six_ion_MIXDER
ninty_five_CI_lower = vector(length = 0)
ninty_five_CI_upper = vector(length = 0)
a = vector(length = 0)
for (i in 2:length(d3)) {
  
  a = CI_function_MIXDER_var(d = c(0, six_ion_MIXDER_var$d[i]), r = rep(1/6, times = 6), L = c(75, 100, 125, 175, 195, 240), Z.b = c(595, 690, 770, 1075, 1245, 1585))
  ninty_five_CI_lower = c(ninty_five_CI_lower, a[1])
  ninty_five_CI_upper = c(ninty_five_CI_upper, a[2])
}
six_ion_MIXDER_var$CI_lower = c(0, ninty_five_CI_lower + 0.00071)
six_ion_MIXDER_var$CI_upper = c(0, ninty_five_CI_upper + 0.00071)

#Get the simple effect additivity MIXDER 
six_ion_MIXDER_var$simpleeffect = IDER(d = 1/6*d3, L = 125, Z.b = 770) + IDER(d = 1/6*d3, L = 175, Z.b = 1075) + IDER(d = 1/6*d3, L = 75, Z.b = 595) + IDER(d = 1/6*d3, L = 100, Z.b = 690) + IDER(d = 1/6*d3, L = 195, Z.b = 1245) + IDER(d = 1/6*d3, L = 240, Z.b = 1585) + 0.00071

#Get the individual IDERS
six_ion_MIXDER_var$oxygen = IDER(d = d3, L = 75, Z.b = 595) + 0.00071
six_ion_MIXDER_var$silicon = IDER(d = d3, L = 100, Z.b = 690) + 0.00071
six_ion_MIXDER_var$titanium = IDER(d = d3, L = 125, Z.b = 770) + 0.00071
six_ion_MIXDER_var$ironsix = IDER(d = d3, L = 175, Z.b = 1075) + 0.00071
six_ion_MIXDER_var$ironfour = IDER(d = d3, L = 195, Z.b = 1245) + 0.00071
six_ion_MIXDER_var$ironthree = IDER(d = d3, L = 240, Z.b = 1585) + 0.00071

#write.csv(six_ion_MIXDER_var, "6ionMonteCarlovar.csv", row.names = F)
```

