---
title: "Hada_lymphocyte"
author: "Peter Wang"
date: "February 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(deSolve) # package for solving differential equations
library(minpack.lm) # package for non-linear regression #rks to laz: I think we probably can just use nls() in stats, not nlsLM from linpack. Please check in R documentation if there is any functional difference at all
library(mvtnorm) #package for calculating confidence intervals by Monte Carlo simulation based on variance-covariance matrices #rks to laz: I added to comment.Please check that my addition is OK.
library(dplyr)
library(ggplot2)
rm(list=ls())
```

##Entering Data
```{r}
#Create dataframes that store the fibroblast WGE simple CA data used in 16Cacao 
#L and Z.b are rounded to the nearest 5.
Oxygen = data.frame(d = c(0, .0125, .025, .05, .075, .1, .2, .3, .4, .8),CA = c(.72, .96, 2.83, 4.7, 4.01, 8.41, 16.8, 40, 42.8, 94.4), ion = "O", Z = 8, L = 75, Z.b = 595)# Some GCR components are high-speed Oxygen nuclei that are almost fully ionized. d=dose; CA are per hundred cells. Z=atomic charge; L=LET; Z.b = Z^2/beta*^2

Si = data.frame(d = c(0, .02, .04, .06, .08, .1, .12, .15, .2, .3, .4, .6, .8, 1, 1.2, 1.5), CA = c(1.08, 2.04, 3.83, 4.57, 5.96, 4.78, 5.48, 13.88, 13.14, 27.0, 25.9, 59.5, 36.8, 81.8, 117.8, 123.2), ion = "Si", Z = 14, L = 100, Z.b = 690)

Fe600 = data.frame(d = c(0, 0.005, .01, .02, .04, .07, .1, .15, .2, .3, .4, .6, 1, 1.5), CA = c(1.01, 2.05, 2.33, 3.9, 3.51, 3.27, 5.71, 10.7, 9.14, 12.2, 21, 24.9, 43.6, 93.9), ion = "Fe600", Z = 26, L = 175, Z.b = 1075) #600 refers to the energy in MeV per atomic mass unit in this Iron beam

big_df = rbind(Oxygen, Si, Fe600)
big_df$error = c(.42, .48, 1.16, 1.36, 0.94, 2.54, 2.65, 5.9, 6.85, 13.6, .21, .34, .70, .95, .68, 1.07, 1.04, 2.38, 1.72, 4.77, 0.87, 9.18, 2.75, 9.85, 17, 13.2, 0.43, 0.48, 0.67, 0.8, 0.73, 0.75, 1.72, 1.95, 2.89, 2.34, 4.37, 5.08, 8.25, 18.8) #error bars for the CA measurementsx

#Next modify the data frame to get rid of the zero dose points. Background CA frequency was determined seperately.
modified_df = big_df[big_df$d != 0, ]
modified_df$CA = modified_df$CA*0.01 #Change it into per cell from per 100 cells
modified_df$error = modified_df$error*0.01
big_df$CA = big_df$CA * 0.01
big_df$error = big_df$error * 0.01
big_df$errorbar_lower = big_df$CA - big_df$error
big_df$errorbar_upper = big_df$CA + big_df$error
```

##NTE Functions for Lymphocytes (from HADA)
Using Hada's as place holders for now. Using nls to recover a rough estimate of eta0 and eta1 from eta. This is obviously not the optimal solution for eta0 and eta but we have to make do with it.
```{r}
eta_1s <- c(0.97, -0.5, -0.75)/100
eta_2s <- c(3.11, 2.94, 1.47)/100
L <- c(175, 100, 75)
#eta <- c(0.46, 0.26, 0.75, 0.07, 1.21)/100
#eta <- c(1.07, 0.79, 1.18, 0.97, 2.32)/100
#L <- c(175, 195, 220, 100, 75)
eta_nte1 <- data.frame(eta = eta_1s, L)
eta_nte2 <- data.frame(eta = eta_2s, L)
eta_function <- function(L, eta0, eta1){
  eta0 * L * exp(-eta1 * L)
}
NTE1_etafit <- nlsLM(eta ~ eta_function(L, eta0, eta1), data = eta_nte1, start = list(eta0 = 0.001, eta1 = 0.01))
NTE2_etafit <- nlsLM(eta ~ eta_function(L, eta0, eta1), data = eta_nte2, start = list(eta0 = 0.001, eta1 = 0.01))
summary(NTE1_etafit)
summary(NTE2_etafit)
```
As expected, they are horrible :)

##New TE and NTE-TE models for lymphocytes
```{r}
d_0=10^-5 # nominal dose where NTE are saturating, so that for d>>d_0 further increases are due to TE

TE_function = function(d, L, alpha, beta) {
#rks to laz and spw. This is proposed new TE-only model for lymphocytes
  Flux=6.242*d/L # Eq. (5a) in 18_dev_bet; a model-independent equation for particle flux
  A = 30 #The area of the cell nucleus for lymphocytes
  H=A*Flux 
  0 + (alpha + beta * Flux)*(1-exp(-H))
}
new_Q_IDER_model_TEonly = nlsLM(CA ~ TE_function(d, L, alpha, beta), data = modified_df, start = list(alpha = 0.5, beta=5), 
                       weights = (1/(modified_df$error)^2))

NTE_Q_function = function(d, L, eta0, eta1, beta) {
  Flux=6.242*d/L # rks to laz and spw. This is proposed NTE-TE model for lymphocytes
  A = 30 #The area of the cell nucleus for lymphocytes
  H=A*Flux 
  eta = eta0*L*exp(-eta1*L) # Eq. 9 in 18dev_bet
  0.0104 + beta*Flux*(1-exp(-H)) + eta*(1-exp(-d/d_0))  #0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^3*d))#don't use
} 
#nls (non-linear least square) method to get the parameters needed (4 parameter estimation)
new_Q_IDER_model = nlsLM(CA ~ NTE_Q_function(d, L, eta0, eta1, beta), data = modified_df, start = list(eta0 = 0.001, eta1 = 0.01, beta=3),
                 weights = (1/(modified_df$error)^2))

NTE_LQ_function = function(d, L, eta0, eta1,alpha, beta) {
  Flux=6.242*d/L # rks to laz and spw. This is proposed NTE-TE model for lymphocytes
  A = 30 #The area of the cell nucleus for lymphocytes
  H=A*Flux 
  eta = eta0*L*exp(-eta1*L) # Eq. 9 in 18dev_bet
  0.0104 +(alpha/d+ beta)*Flux*(1-exp(-H)) + eta*(1-exp(-d/d_0)) 
} 
new_LQ_IDER_model = nlsLM(CA ~ NTE_LQ_function(d, L, eta0, eta1,alpha, beta), data = modified_df, start = list(eta0 = 0.001, eta1 = 0.01, alpha=0.3, beta=2), 
                       weights = (1/(modified_df$error)^2))
```

##IDER
```{r}
IDER = function(d, L, Z.b, eta0, eta1, sig0, kap) {
  Flux=6.242*d/L
  A = 30 #The area of the cell nucleus for lymphocytes
  H=A*Flux 
  P = (1-exp(-Z.b/kap))^2 #Eq. (7A) in 18_dev_bet; dimensionless "probability"; makes sense for kap > 0
  sig = sig0*P + 0.041/6.24*L*(1-P) # Eq. (7B) in 18_dev_bet
  eta = eta0*L*exp(-eta1*L) # Eq. 9 in 18dev_bet
 0.0104 + sig*Flux*(1-exp(-H)) + eta*(1-exp(-d/d_0))  #0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^3*d))#don't use
} 
IDER_model = nlsLM(CA ~ IDER(d, L, Z.b, eta0, eta1, sig0, kap), data = modified_df, start = list(eta0 = 0.001, eta1 = 0.01, sig0 = 15, kap = 445), 
                   weights = (1/(modified_df$error)^2))
calibrated_coef=coef(IDER_model)
```

First step Results
```{r}
summary(IDER_model, cor = T)
summary(new_Q_IDER_model_TEonly)
summary(new_Q_IDER_model)
summary(new_LQ_IDER_model)
```

##AIC & BIC
```{r}
L_TE <- resid(new_Q_IDER_model_TEonly) ** 2
L_NTE_Q <- resid(new_Q_IDER_model) ** 2
L_NTE_LQ <- resid(new_LQ_IDER_model) ** 2
L_IDER <- resid(IDER_model) ** 2
#Since all models are weighted least square regression, will weight our model with our weights to get the WRSS (weighted residual squared sum)
WRSS_TE = sum((1/modified_df$error^2)*L_TE)
WRSS_NTE_Q = sum((1/modified_df$error^2)*L_NTE_Q)
WRSS_NTE_LQ = sum((1/modified_df$error^2)*L_NTE_LQ)
WRSS_IDER = sum((1/modified_df$error^2)*L_IDER)

#functions for AIC and BIC calculation for Weighted Least Square regression
AIC_function = function(RSS, k = 4, n = length(modified_df[ , 1])) {
  n + n*log(2*pi) + n*log(RSS/n) + 2*(k+1)
}

BIC_function = function(n = length(modified_df[, 1]), k = 4, RSS) {
  n + n*log(2*pi) + n*log(RSS/n) + log(n)*(k+1)
}
TE_AIC = AIC_function(RSS = WRSS_TE, k = 2)
NTE_Q_AIC = AIC_function(RSS = WRSS_NTE_Q, k = 3)
NTE_LQ_AIC = AIC_function(RSS = WRSS_NTE_LQ)
IDER_AIC = AIC_function(RSS = WRSS_IDER)
TE_BIC = BIC_function(RSS = WRSS_TE, k = 2)
NTE_Q_BIC = BIC_function(RSS = WRSS_NTE_Q, k = 3)
NTE_LQ_BIC = BIC_function(RSS = WRSS_NTE_LQ)
IDER_BIC = BIC_function(RSS = WRSS_IDER)

information_critera_df = data.frame(Model = c("TE model","NTE_Q model", "NTE_LQ model", "IDER model"), AIC = c(TE_AIC, NTE_Q_AIC, NTE_LQ_AIC, IDER_AIC), BIC = c(TE_BIC, NTE_Q_BIC, NTE_LQ_BIC, IDER_BIC))
arrange(information_critera_df, AIC)
```

TE is 2nd to best, in terms of AIC and BIC, and it is really close to the LQ model.

##Baseline no-synergy/no-antagonism MIXTE
```{r}
alpha0 <- as.numeric(coef(new_Q_IDER_model_TEonly)[1])
beta0 <- as.numeric(coef(new_Q_IDER_model_TEonly)[2])
TE_O <- function(d) TE_function(d, L = 75, alpha = alpha0, beta = beta0)
TE_Si <- function(d) TE_function(d, L = 100, alpha = alpha0, beta = beta0)
TE_Fe600 <- function(d) TE_function(d, L = 175, alpha = alpha0, beta = beta0)

ggplot(modified_df[modified_df$ion == "O", ], aes(x = d, y = CA)) + geom_point() + stat_function(fun = TE_O)
ggplot(modified_df[modified_df$ion == "Si", ], aes(x = d, y = CA)) + geom_point() + stat_function(fun = TE_Si)
ggplot(modified_df[modified_df$ion == "Fe600", ], aes(x = d, y = CA)) + geom_point() + stat_function(fun = TE_Fe600)
```

```{r}
MIXTE_function = function(r, L, Z.b, d = seq(0, 0.2, by = 0.001), alpha = alpha0, beta = beta0){
  dE = function(yini, State, Pars){
    n = length(L)
    beta = beta0
    with(as.list(c(State, Pars)), {
      u = numeric(n)
      for (i in 1:n){
        u[i] = uniroot(function(d) {(alpha + beta *6.242*d/L[i])*(1 - exp(-30*6.242*d/L[i])) - I}, lower = 0, upper = 0.4, extendInt = "yes", tol = 10^-10)$root
      }
      dI = numeric(n)
      H = numeric(n)
      for(i in 1:n){
        H[i] = 6.24*30*u[i]/L[i]
        dI[i] = r[i]*(6.24/L[i] * exp(-H[i]) * (beta*(exp(H[i]) + H[i] - 1) + 30 * alpha)) #Partial derivative of TE function over d. This is always 0 when d = 0 though.
      }
      dI = sum(dI)
      return(list(c(dI)))
    })
  }
  pars = NULL; yini = c(I = 0); d = d
  out = ode(yini,times = d, dE, pars, method = "radau")
  return(out)
}

```

```{r}
#Here is the TE function again for individual dose
TE_function = function(d, L, alpha, beta) {
  Flux=6.242*d/L # Eq. (5a) in 18_dev_bet; a model-independent equation for particle flux
  A = 30 #The area of the cell nucleus for lymphocytes
  H=A*Flux 
  0 + (alpha + beta*Flux)*(1-exp(-H))
}
r = rep(1/3, 3); L = c(75, 100, 175); Z.b = c(595, 690, 1075); dose = seq(0,.4,by=0.001)
MX = MIXTE_function(r, L, Z.b, d = dose)
plot(MX[,1],MX[,2],type='l',bty='l',col='red',ann='F',ylim=c(0,0.5))
for (ii in 1:length(L)){lines(dose,TE_function(dose,L[ii], alpha = alpha0, beta = beta0),col='green')}
#SEA
SEA=function(d){
  TE_function(d = d/3,L[1], alpha = alpha0, beta = beta0) + TE_function(d/3,L[2],alpha = alpha0, beta = beta0)+TE_function(d/3,L[3],alpha = alpha0, beta = beta0)
}
lines(dose,SEA(dose),lty=2)
```
##Getting a sample of parameters (n = 500)
```{r}
sig = vcov(new_Q_IDER_model_TEonly)
set.seed(10)
monte_carlo_parameters = rmvnorm(n = 500, mean = c(alpha = alpha0, beta = beta0), sigma = sig)
alpha0_MC = monte_carlo_parameters[, 1]
beta0_MC = monte_carlo_parameters[, 2]
```

##Monte Carlo CI
```{r}
CI_function_MIXTE = function(d, r, interval = 0.95, L, Z.beta, alphas = alpha0_MC, betas = beta0_MC) {
  MIXTE_curve = list(length = 0)
  for (i in 1:500) {
    MIXTE_curve[[i]] = MIXTE_function(r, L, Z.b, d = d, alpha = alphas[i], beta = betas[i])
  }
  info = vector(length = 0)
  for (i in 1:500) {
    info = c(info, MIXTE_curve[[i]][, 2][2])
  }
  info = sort(info)
  lower_bound = quantile(info, (1-interval)/2)
  upper_bound = quantile(info, 1 - (1-interval)/2)
  CI = c(lower_bound, upper_bound)
  return(CI)
}
```

##2-ion Mix, Silicon and Fe600
```{r}
out = MIXTE_function(r = rep(1/2, times = 2), L = c(100, 175), Z.b = c(690, 1075), d = c(seq(0, 0.009, 0.001), seq(0.01, 0.5, by = 0.01)))
two_ion_MIXTE1 = data.frame(d = out[, 1], CA = out[, 2])
two_ion_MIXTE2 = data.frame(d = out[, 1][seq(11,60, by = 5)], CA = out[, 2][seq(11,60, by = 5)])
d1 =two_ion_MIXTE1$d
d2 =two_ion_MIXTE2$d
```

```{r}
v2 <- data.frame(lower = vector(length = length(d2)),upper = vector(length = length(d2)))
#Then the 95% CI multivariate MC simulated ribbon
ninty_five_CI_lower = vector(length = 0)
ninty_five_CI_upper = vector(length = 0)
a = vector(length = 0)
for (i in 1:length(d2)) {
  a = CI_function_MIXTE(d = c(0, d2[i]), r = rep(1/2, times = 2),  L = c(100, 175), Z.b = c(690, 1075))
  v2$lower[i-1] = a[1]
  v2$upper[i-1] = a[2]
  print(a)
  ninty_five_CI_lower = c(ninty_five_CI_lower, a[1])
  ninty_five_CI_upper = c(ninty_five_CI_upper, a[2])
}
two_ion_MIXTE2$CI_lower = c(ninty_five_CI_lower)
two_ion_MIXTE2$CI_upper = c(ninty_five_CI_upper)

#Get the simple effect additivity MIXTE
two_ion_MIXTE2$simpleeffect = TE_function(d = 0.5*d2, L = 100, alpha = alpha0, beta = beta0) + TE_function(d = 0.5*d2, L = 175, alpha = alpha0, beta = beta0)
#Get the individual TE_functionS
two_ion_MIXTE2$silicon = TE_function(d = d2, L = 100, alpha = alpha0, beta = beta0)
two_ion_MIXTE2$ironsix = TE_function(d = d2, L = 175, alpha = alpha0, beta = beta0)

CA2 <- two_ion_MIXTE2$CA
simpleeffect2 <- two_ion_MIXTE2$simpleeffect
silicon2 <- two_ion_MIXTE2$silicon
ironsix2 <- two_ion_MIXTE2$ironsix
plot(x = d2 * 100, y = CA2 * 100, type = "l", col = "red")
lines(x = d2 * 100, y = simpleeffect2 * 100, col = "black", lty = 2, lwd = 0.5) + 
lines(x = d2 * 100, y = silicon2* 100, col = "green")  
lines(x = d2 * 100, y = ironsix2* 100, col = "green")
lines(x= d2*100 , y = two_ion_MIXTE2$CI_upper * 100, lty = 'dashed', col = 'red')
lines(x= d2*100 , y = two_ion_MIXTE2$CI_lower * 100, lty = 'dashed', col = 'red')
polygon(c(d2*100,rev(d2*100)),c(two_ion_MIXTE2$CI_lower * 100, rev(two_ion_MIXTE2$CI_upper * 100)),col = rgb(1, 0, 0,0.5), border = NA)
```

